On the presentation of orthogonal groups over polynomial rings

### 2019-04-30 dl-paper.tex
Abridged Lemma 12

It remains to verify the assertion for the remaining generator $z_\alpha(f, gX)$ of type 2. Substituting in~\eqref{Z5} of~\cref{Crels} $s := -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ we obtain that
\begin{multline} \nonumber
 z_{\alpha+\beta}(-\epsilon fX, -\epsilon g) = x_\alpha( -f) x_{-\beta}(- f g) \cdot x_{\beta}( f gX^2) \cdot x_{\alpha+\beta}(-\epsilon f X) \cdot \\ \cdot z_\alpha(f,  gX) \cdot x_{-\alpha}(fg^2X^2) \cdot x_{-\alpha-\beta}(\epsilon f g^2 X) \cdot z_{-\beta}(fg, -X), 
\end{multline}
where $\epsilon = N_{\alpha,\beta}$. 
Expressing $z_{\alpha}(f, gX)$ through other terms
\begin{multline} \nonumber
 z_\alpha(f, gX) = 
 x_{\alpha+\beta}(\epsilon f X) \cdot
 x_{\beta}(-f gX^2) \cdot
 x_{-\beta}(f g) \cdot
 x_\alpha(f) \cdot \\ \cdot
 z_{\alpha+\beta}(-\epsilon fX, -\epsilon g) \cdot 
 z_{-\beta}(-fg, -X) \cdot
 x_{-\alpha-\beta}(-\epsilon f g^2 X) \cdot
 x_{-\alpha}(-fg^2X^2) \cdot
\end{multline}
we conclude that the factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. 
\end{proof}

>>>>

It remains to verify the assertion for the remaining generator $z_\alpha(f, gX)$ of type 2. Substituting in~\eqref{Z5} of~\cref{Crels} $s = -\epsilon f$, $\xi = -\epsilon g$, $\eta=X$ and expressing $z_\alpha(f, gX)$ through other terms we obtain that
\begin{multline} \nonumber
 z_\alpha(f, gX) = 
 x_{\alpha+\beta}(\epsilon f X) \cdot
 x_{\beta}(-f gX^2) \cdot
 x_{-\beta}(f g) \cdot
 x_\alpha(f) \cdot \\ \cdot
 z_{\alpha+\beta}(-\epsilon fX, -\epsilon g) \cdot 
 z_{-\beta}(-fg, -X) \cdot
 x_{-\alpha-\beta}(-\epsilon f g^2 X) \cdot
 x_{-\alpha}(-fg^2X^2),
\end{multline}
where $\epsilon = N_{\alpha,\beta}$. 
The factors in the right-hand side are generators of type 1, 1, 2, 2, 1, 2, 1, 4. It is clear, that conjugation by $x_{\alpha}(aX^{-1})$ acts trivially on the fourth factor $x_\alpha(f)$, while for the other factors we have already verified that their conjugates belong to $P_{\alpha}(0)$. 
\end{proof}
